---
title: "Assigment 1"
author: "Shengsheng He"
date: "2023/3/09"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE, warning = FALSE)
```

# Top 3 Dogs with smiling picture

* Two Golden retriever (younger and older).
* one Shiba Inu.

```{r}
library(magick)
dog1 <- image_read('1.jfif') # name the image
dog2 <- image_read('2.jfif')
dog3 <- image_read('3.jfif')
image_append(c(dog1,dog2,dog3))
meme <- image_append(c(dog1,dog2,dog3))
image_write(meme, "my_meme.png") # save




```

The Golden retriever are my favorite type, cute and smart. While I was smiling to my dog, she will respond to me a smile as well. The relationship between human and dog are the pure, I wanted to pass the happiness between the pet and human to everyone by this meme.  


```{r}
library(magick)
dog1 <- image_read('1.jfif') # name the image
dog2 <- image_read('2.jfif')
dog3 <- image_read('3.jfif')
animation <- c(dog1,dog2,dog3)
animation %>%
   image_animate(fps = 1) # animate the image
image_write(animation, "my_animation.gif")


```
I animate the meme images into fps = 1, which the image will all the smiling face I love and I believe it will make everyone happy!

The github is helping me a lot with to understand the data can be collect and remake it into my own creative, so many works that other people post on it is intersting to read and look, I will try to do some other things at github to improve my skills to dealing with data.  
My github page:[github]('https://github.com/She840/stats-220-new.git') 




```{css}
p {font-wight: bold; }

```
