---
title: "Assigment 1"
author: "Shengsheng He"
date: "2023/3/09"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE, warning = FALSE)
```

# Top 3 Dogs with smiling picture

* Two Golden retriever (younger and older).
* one Shiba Inu.

```{r, eval=FALSE}
library(magick)
dog1 <- image_read('1.jfif') # name the image
dog2 <- image_read('2.jfif')
dog3 <- image_read('3.jfif')
meme <- image_append(c(dog1,dog2,dog3))
image_write(meme, "my_meme.png") # save




```

The Golden retriever are my favorite type, cute and smart. While I was smiling to my dog, she will respond to me a smile as well. The relationship between human and dog are the pure, I wanted to pass the happiness between the pet and human to everyone by this meme.  


```{r}
library(magick)
dog1 <- image_read('1.jfif') # name the image
dog2 <- image_read('2.jfif')
dog3 <- image_read('3.jfif')
animation <- c(dog1,dog2,dog3)
animation %>%
   image_animate(fps = 1) # animate the image
image_write(animation, "my_animation.gif")


```
I animate the meme images into fps = 1, which the image will all the smiling face I love and I believe it will make everyone happy!


```{css}
p {font-wight: bold; }

```
